---
title: "dissertation"
output: html_document
date: "2024-06-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, echo=TRUE, message = FALSE, warning = FALSE}
# set working directory
```
# packages
```{r, warning=FALSE, include=FALSE}
if(!require("dplyr")) install.packages("dplyr")
if(!require("readr")) install.packages("readr")
if(!require("sf")) install.packages("sf")
if(!require("sp")) install.packages("sp")
if(!require("raster")) install.packages("raster")
if(!require("terra")) install.packages("terra")
if(!require("exactextractr")) install.packages("exactextractr")
if(!require("ggplot2")) install.packages("ggplot2")
if(!require("viridis")) install.packages("viridis")
if(!require("tmap")) install.packages("tmap")
if(!require("RColorBrewer")) install.packages("RColorBrewer")
if(!require("osmdata")) install.packages("osmdata")
if(!require("ggmap")) install.packages("ggmap")
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("spDataLarge")) install.packages("spDataLarge", repos = "https://geocompr.r-universe.dev")
if(!require("ggspatial")) install.packages("ggspatial")
if(!require("tidycensus")) install.packages("tidycensus")
if(!require("gridExtra")) install.packages("gridExtra")
if(!require("cowplot")) install.packages("cowplot")
if(!require("biscale")) install.packages("biscale")
```
```{r include=FALSE}
library(readxl)
library(readr)
library(dplyr)
library(fixest)
library(stringr)
library(sf)
library(sp)
library(raster)
library(ggplot2)
library(viridis)
library(tmap)
library(RColorBrewer)
library(ggmap)
library(tidyverse)
library(ggspatial)
library(plm)
library(data.table)
library(pglm)
library(MASS)
```

# data preparation
## folder path
```{r}
path_to_folder <- "/Users/wangyue/Desktop/dissertation_data/"
```

## shenzhen shapefile
```{r, message=FALSE, warning=FALSE}
shenzhen <- st_read(paste0(path_to_folder, "/shenzhen/440300.shp") )
shenzhen <- shenzhen %>%
  dplyr::select(id, name, geometry)

shenzhen <- st_set_crs(shenzhen, 4547)

ggplot(data = shenzhen) +
  geom_sf(fill = NA, color = "black") +  
  theme_minimal()  +
   theme(line = element_blank(), 
        axis.text=element_blank())
```

## poi data (Cainiao stations)
import shapefile
```{r, include=FALSE}
poi2013 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2013poi.shp"))
poi2014 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2014poi.shp"))
poi2015 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2015poi.shp"))
poi2016 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2016poi.shp"))
poi2017 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2017poi.shp"))
poi2018 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2018poi.shp"))
poi2019 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2019poi.shp"))
poi2020 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2020poi.shp"))
poi2021 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2021poi.shp"))
poi2022 <- st_read(paste0(path_to_folder, "/shenzhen_poi/shp/2022poi.shp"))

poi2013 <- st_transform(poi2013, crs = 4547)
poi2014 <- st_transform(poi2014, crs = 4547)
poi2015 <- st_transform(poi2015, crs = 4547)
poi2016 <- st_transform(poi2016, crs = 4547)
poi2017 <- st_transform(poi2017, crs = 4547)
poi2018 <- st_transform(poi2018, crs = 4547)
poi2019 <- st_transform(poi2019, crs = 4547)
poi2020 <- st_transform(poi2020, crs = 4547)
poi2021 <- st_transform(poi2021, crs = 4547)
poi2022 <- st_transform(poi2022, crs = 4547)
```

### filter poi data
```{r, warning=FALSE}
poi2013 <- poi2013 %>%
  dplyr::select(name, adname, adcode, geometry)

poi2014 <- poi2014 %>%
  dplyr::select(NAME, COUNTY, CODE, geometry) %>%
  rename(name = NAME, adname = COUNTY, adcode = CODE)

poi2015 <- poi2015 %>%
  dplyr::select(NAME, COUNTY, CODE, geometry) %>%
  rename(name = NAME, adname = COUNTY, adcode = CODE)

poi2016 <- poi2016 %>%
  dplyr::select(NAME, COUNTY, CODE, geometry) %>%
  rename(name = NAME, adname = COUNTY, adcode = CODE)

poi2017 <- poi2017 %>%
  dplyr::select(name, adname, adcode, geometry) %>%
    filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站"))

poi2018 <- poi2018 %>%
  filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站") | str_detect(name, "智能柜")) %>%
  dplyr::select(name, adname, adcode, geometry) 

poi2019 <- poi2019 %>%
  filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站") | str_detect(name, "智能柜")) %>%
  dplyr::select(name, adname, adcode, geometry) 

poi2020 <- poi2020 %>%
  filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站") | str_detect(name, "智能柜") | str_detect(name, "速递易柜")) %>%
  dplyr::select(name, adname, adcode, geometry) 

poi2021 <- poi2021 %>%
  filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站") | str_detect(name, "智能柜") | str_detect(name, "速递易柜") | str_detect(name, "快递超市")) %>%
  dplyr::select(name, adname, adcode, geometry)

poi2022 <- poi2022 %>%
  filter(str_detect(name, "菜鸟") | str_detect(name, "自提柜") | str_detect(name, "快递柜") | str_detect(name, "驿站") | str_detect(name, "智能柜") | str_detect(name, "速递易柜") | str_detect(name, "快递超市") | str_detect(name, "快递点") | str_detect(name, "送货柜")) %>%
  dplyr::select(name, adname, adcode, geometry) 
```

## nighttime light data
###Li(2020)
####2013
```{r, warning=FALSE}
Li2013 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2013.tif"))
Li2013 <- crop(Li2013, shenzhen)
Li2013 <- mask(Li2013, shenzhen)

Li2013_df <- as.data.frame(Li2013, xy = TRUE, na.rm = TRUE)
names(Li2013_df)[3] <- "value"  

Li2013_df <- Li2013_df %>%
  filter(value > 7)

Li2013_map <- ggplot() +
  geom_raster(data = Li2013_df, aes(x = x, y = y, fill = value)) +
  scale_fill_gradientn(
    colors = c("white", "lightblue", "blue", "darkblue"),
    values = scales::rescale(c(0, 30, 50, 60, 63)),  
    limits = c(min(0), max(Li2013_df$value, na.rm = TRUE)),
    oob = scales::squish
  ) +
  coord_sf() +
  theme_void() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)  # Center the title
  ) +
  labs(fill = "DN values") +
  ggtitle("Nighttime Light Value in 2013") 
Li2013_map
```

####2014
```{r, warning=FALSE}
Li2014 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2014.tif"))
Li2014 <- crop(Li2014, shenzhen)
Li2014 <- mask(Li2014, shenzhen)

Li2014_df <- as.data.frame(Li2014, xy = TRUE, na.rm = TRUE)
names(Li2014_df)[3] <- "value"  
Li2014_df <- Li2014_df %>%
  filter(value > 7)
```

####2015
```{r, warning=FALSE}
Li2015 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2015.tif"))
Li2015 <- crop(Li2015, shenzhen)
Li2015 <- mask(Li2015, shenzhen)

Li2015_df <- as.data.frame(Li2015, xy = TRUE, na.rm = TRUE)
names(Li2015_df)[3] <- "value"  
Li2015_df <- Li2015_df %>%
  filter(value > 7)
```

#### 2016
```{r, warning=FALSE}
Li2016 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2016.tif"))
Li2016 <- crop(Li2016, shenzhen)
Li2016 <- mask(Li2016, shenzhen)

Li2016_df <- as.data.frame(Li2016, xy = TRUE, na.rm = TRUE)
names(Li2016_df)[3] <- "value"  
Li2016_df <- Li2016_df %>%
  filter(value > 7)

Li2016_map <- ggplot() +
  geom_raster(data = Li2016_df, aes(x = x, y = y, fill = value)) +
  scale_fill_gradientn(
    colors = c("white", "lightblue", "blue", "darkblue"),
    values = scales::rescale(c(0, 30, 50, 60, 63)),  
    limits = c(min(0), max(Li2016_df$value, na.rm = TRUE)),
    oob = scales::squish
  ) +
  coord_sf() +
  theme_void() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5) 
  ) +
  labs(fill = "DN values") +
  ggtitle("Nighttime Light Value in 2016")
Li2016_map
```


####2017
```{r, warning=FALSE}
Li2017 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2017.tif"))
Li2017 <- crop(Li2017, shenzhen)
Li2017 <- mask(Li2017, shenzhen)

Li2017_df <- as.data.frame(Li2017, xy = TRUE, na.rm = TRUE)
names(Li2017_df)[3] <- "value"  
Li2017_df <- Li2017_df %>%
  filter(value > 7)
```

####2018
```{r, warning=FALSE}
Li2018 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2018.tif"))
Li2018 <- crop(Li2018, shenzhen)
Li2018 <- mask(Li2018, shenzhen)

Li2018_df <- as.data.frame(Li2018, xy = TRUE, na.rm = TRUE)
names(Li2018_df)[3] <- "value"  
Li2018_df <- Li2018_df %>%
  filter(value > 7)
```

#### 2019
```{r, warning=FALSE,message=FALSE}
Li2019 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2019.tif"))
Li2019 <- crop(Li2019, shenzhen)
Li2019 <- mask(Li2019, shenzhen)

Li2019_df <- as.data.frame(Li2019, xy = TRUE, na.rm = TRUE)
names(Li2019_df)[3] <- "value"  
Li2019_df <- Li2019_df %>%
  filter(value > 7)

Li2019_map <- ggplot() +
  geom_raster(data = Li2019_df, aes(x = x, y = y, fill = value)) +
  scale_fill_gradientn(
    colors = c("white", "lightblue", "blue", "darkblue"),
    values = scales::rescale(c(0, 30, 50, 60, 63)), 
    limits = c(min(0), max(Li2019_df$value, na.rm = TRUE)),
    oob = scales::squish
  ) +
  coord_sf() +
  theme_void() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)  # Center the title
  ) +
  labs(fill = "DN values") +
  ggtitle("Nighttime Light Value in 2019")
Li2019_map
```


####2020
```{r, warning=FALSE}
Li2020 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2020.tif"))
Li2020 <- crop(Li2020, shenzhen)
Li2020 <- mask(Li2020, shenzhen)

Li2020_df <- as.data.frame(Li2020, xy = TRUE, na.rm = TRUE)
names(Li2020_df)[3] <- "value"  
Li2020_df <- Li2020_df %>%
  filter(value > 7)
```

####2021
```{r, warning=FALSE}
Li2021 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2021.tif"))
Li2021 <- crop(Li2021, shenzhen)
Li2021 <- mask(Li2021, shenzhen)

Li2021_df <- as.data.frame(Li2021, xy = TRUE, na.rm = TRUE)
names(Li2021_df)[3] <- "value"  
Li2021_df <- Li2021_df %>%
  filter(value > 7)
```

#### 2022
```{r, warning=FALSE}
Li2022 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2022.tif"))
Li2022 <- crop(Li2022, shenzhen)
Li2022 <- mask(Li2022, shenzhen)

Li2022_df <- as.data.frame(Li2022, xy = TRUE, na.rm = TRUE)
names(Li2022_df)[3] <- "value"  
Li2022_df <- Li2022_df %>%
  filter(value > 7)

Li2022_map <- ggplot() +
  geom_raster(data = Li2022_df, aes(x = x, y = y, fill = value)) +
  scale_fill_gradientn(
    colors = c("white", "lightblue", "blue", "darkblue"),
    values = scales::rescale(c(0, 30, 50, 60, 63)), 
    limits = c(min(0), max(Li2022_df$value, na.rm = TRUE)),
    oob = scales::squish
  ) +
  coord_sf() +
  theme_void() +
  theme(
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)  
  ) +
  labs(fill = "DN values") +
  ggtitle("Nighttime Light Value in 2022")
Li2022_map
```


##  measurement of parcel stations
### nearest distance to parcel stations
```{r}
Li2013 <- rasterToPoints(Li2013, spatial = TRUE)
Li2013 <- st_as_sf(Li2013)
Li2013 <- st_transform(Li2013, crs = 4547)
names(Li2013)[1] <- "value"  
Li2013 <- Li2013 %>%
  filter(value > 7)


Li2014 <- rasterToPoints(Li2014, spatial = TRUE)
Li2014 <- st_as_sf(Li2014)
Li2014 <- st_transform(Li2014, crs = 4547)
names(Li2014)[1] <- "value"  
Li2014 <- Li2014 %>%
  filter(value > 7)

Li2015 <- rasterToPoints(Li2015, spatial = TRUE)
Li2015 <- st_as_sf(Li2015)
Li2015 <- st_transform(Li2015, crs = 4547)
names(Li2015)[1] <- "value"  
Li2015 <- Li2015 %>%
  filter(value > 7)

Li2016 <- rasterToPoints(Li2016, spatial = TRUE)
Li2016 <- st_as_sf(Li2016)
Li2016 <- st_transform(Li2016, crs = 4547)
names(Li2016)[1] <- "value"  
Li2016 <- Li2016 %>%
  filter(value > 7)

Li2017 <- rasterToPoints(Li2017, spatial = TRUE)
Li2017 <- st_as_sf(Li2017)
Li2017 <- st_transform(Li2017, crs = 4547)
names(Li2017)[1] <- "value"  
Li2017 <- Li2017 %>%
  filter(value > 7)

Li2018 <- rasterToPoints(Li2018, spatial = TRUE)
Li2018 <- st_as_sf(Li2018)
Li2018 <- st_transform(Li2018, crs = 4547)
names(Li2018)[1] <- "value"  
Li2018 <- Li2018 %>%
  filter(value > 7)

Li2019 <- rasterToPoints(Li2019, spatial = TRUE)
Li2019 <- st_as_sf(Li2019)
Li2019 <- st_transform(Li2019, crs = 4547)
names(Li2019)[1] <- "value"  
Li2019 <- Li2019 %>%
  filter(value > 7)

Li2020 <- rasterToPoints(Li2020, spatial = TRUE)
Li2020 <- st_as_sf(Li2020)
Li2020 <- st_transform(Li2020, crs = 4547)
names(Li2020)[1] <- "value"  
Li2020 <- Li2020 %>%
  filter(value > 7)

Li2021 <- rasterToPoints(Li2021, spatial = TRUE)
Li2021 <- st_as_sf(Li2021)
Li2021 <- st_transform(Li2021, crs = 4547)
names(Li2021)[1] <- "value"  
Li2021 <- Li2021 %>%
  filter(value > 7)

Li2022 <- rasterToPoints(Li2022, spatial = TRUE)
Li2022 <- st_as_sf(Li2022)
Li2022 <- st_transform(Li2022, crs = 4547)
names(Li2022)[1] <- "value"  
Li2022 <- Li2022 %>%
  filter(value > 7)
```

```{r}
distances <- st_distance(Li2013, poi2013, by_element = FALSE)
Li2013$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2014, poi2014, by_element = FALSE)
Li2014$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2015, poi2015, by_element = FALSE)
Li2015$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2016, poi2016, by_element = FALSE)
Li2016$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2017, poi2017, by_element = FALSE)
Li2017$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2018, poi2018, by_element = FALSE)
Li2018$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2019, poi2019, by_element = FALSE)
Li2019$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2020, poi2020, by_element = FALSE)
Li2020$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2021, poi2021, by_element = FALSE)
Li2021$nearest_station_distance <- apply(distances, 1, min)

distances <- st_distance(Li2022, poi2022, by_element = FALSE)
Li2022$nearest_station_distance <- apply(distances, 1, min)
```

```{r}
Li2013 <- Li2013 %>%
  rename(ntl = value)
Li2013$year <- 2013

Li2014 <- Li2014 %>%
  rename(ntl = value)
Li2014$year <- 2014

Li2015 <- Li2015 %>%
  rename(ntl = value)
Li2015$year <- 2015

Li2016 <- Li2016 %>%
  rename(ntl = value)
Li2016$year <- 2016

Li2017 <- Li2017 %>%
  rename(ntl = value)
Li2017$year <- 2017

Li2018 <- Li2018 %>%
  rename(ntl = value)
Li2018$year <- 2018

Li2019 <- Li2019 %>%
  rename(ntl = value)
Li2019$year <- 2019

Li2020 <- Li2020 %>%
  rename(ntl = value)
Li2020$year <- 2020

Li2021 <- Li2021 %>%
  rename(ntl = value)
Li2021$year <- 2021

Li2022 <- Li2022 %>%
  rename(ntl = value)
Li2022$year <- 2022
```

```{r}
nearest_dis <- bind_rows(Li2013, Li2014, Li2015, Li2016, Li2017, Li2018, Li2019, Li2020, Li2021, Li2022)
```

### buffer
##### re-load dataset
```{r}
Li2013 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2013.tif"))
Li2013 <- crop(Li2013, shenzhen)
Li2013 <- mask(Li2013, shenzhen)
Li2013 <- rasterToPoints(Li2013, spatial = TRUE)
Li2013 <- st_as_sf(Li2013)
Li2013 <- st_transform(Li2013, crs = 4547)
names(Li2013)[1] <- "value"  
Li2013 <- Li2013 %>%
  filter(value > 7)

Li2014 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2014.tif"))
Li2014 <- crop(Li2014, shenzhen)
Li2014 <- mask(Li2014, shenzhen)
Li2014 <- rasterToPoints(Li2014, spatial = TRUE)
Li2014 <- st_as_sf(Li2014)
Li2014 <- st_transform(Li2014, crs = 4547)
names(Li2014)[1] <- "value"  
Li2014 <- Li2014 %>%
  filter(value > 7)

Li2015 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2015.tif"))
Li2015 <- crop(Li2015, shenzhen)
Li2015 <- mask(Li2015, shenzhen)
Li2015 <- rasterToPoints(Li2015, spatial = TRUE)
Li2015 <- st_as_sf(Li2015)
Li2015 <- st_transform(Li2015, crs = 4547)
names(Li2015)[1] <- "value"  
Li2015 <- Li2015 %>%
  filter(value > 7)

Li2016 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2016.tif"))
Li2016 <- crop(Li2016, shenzhen)
Li2016 <- mask(Li2016, shenzhen)
Li2016 <- rasterToPoints(Li2016, spatial = TRUE)
Li2016 <- st_as_sf(Li2016)
Li2016 <- st_transform(Li2016, crs = 4547)
names(Li2016)[1] <- "value"  
Li2016 <- Li2016 %>%
  filter(value > 7)

Li2017 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2017.tif"))
Li2017 <- crop(Li2017, shenzhen)
Li2017 <- mask(Li2017, shenzhen)
Li2017 <- rasterToPoints(Li2017, spatial = TRUE)
Li2017 <- st_as_sf(Li2017)
Li2017 <- st_transform(Li2017, crs = 4547)
names(Li2017)[1] <- "value"  
Li2017 <- Li2017 %>%
  filter(value > 7)

Li2018 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2018.tif"))
Li2018 <- crop(Li2018, shenzhen)
Li2018 <- mask(Li2018, shenzhen)
Li2018 <- rasterToPoints(Li2018, spatial = TRUE)
Li2018 <- st_as_sf(Li2018)
Li2018 <- st_transform(Li2018, crs = 4547)
names(Li2018)[1] <- "value"  
Li2018 <- Li2018 %>%
  filter(value > 7)

Li2019 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2019.tif"))
Li2019 <- crop(Li2019, shenzhen)
Li2019 <- mask(Li2019, shenzhen)
Li2019 <- rasterToPoints(Li2019, spatial = TRUE)
Li2019 <- st_as_sf(Li2019)
Li2019 <- st_transform(Li2019, crs = 4547)
names(Li2019)[1] <- "value"  
Li2019 <- Li2019 %>%
  filter(value > 7)

Li2020 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2020.tif"))
Li2020 <- crop(Li2020, shenzhen)
Li2020 <- mask(Li2020, shenzhen)
Li2020 <- rasterToPoints(Li2020, spatial = TRUE)
Li2020 <- st_as_sf(Li2020)
Li2020 <- st_transform(Li2020, crs = 4547)
names(Li2020)[1] <- "value"  
Li2020 <- Li2020 %>%
  filter(value > 7)

Li2021 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2021.tif"))
Li2021 <- crop(Li2021, shenzhen)
Li2021 <- mask(Li2021, shenzhen)
Li2021 <- rasterToPoints(Li2021, spatial = TRUE)
Li2021 <- st_as_sf(Li2021)
Li2021 <- st_transform(Li2021, crs = 4547)
names(Li2021)[1] <- "value"  
Li2021 <- Li2021 %>%
  filter(value > 7)

Li2022 <- raster(paste0(path_to_folder, "/nighttime_light/Li2020/2022.tif"))
Li2022 <- crop(Li2022, shenzhen)
Li2022 <- mask(Li2022, shenzhen)
Li2022 <- rasterToPoints(Li2022, spatial = TRUE)
Li2022 <- st_as_sf(Li2022)
Li2022 <- st_transform(Li2022, crs = 4547)
names(Li2022)[1] <- "value"  
Li2022 <- Li2022 %>%
  filter(value > 7)
```

```{r}
Li2013 <- Li2013 %>%
  rename(ntl = value)
Li2013$year <- 2013

Li2014 <- Li2014 %>%
  rename(ntl = value)
Li2014$year <- 2014

Li2015 <- Li2015 %>%
  rename(ntl = value)
Li2015$year <- 2015

Li2016 <- Li2016 %>%
  rename(ntl = value)
Li2016$year <- 2016

Li2017 <- Li2017 %>%
  rename(ntl = value)
Li2017$year <- 2017

Li2018 <- Li2018 %>%
  rename(ntl = value)
Li2018$year <- 2018

Li2019 <- Li2019 %>%
  rename(ntl = value)
Li2019$year <- 2019

Li2020 <- Li2020 %>%
  rename(ntl = value)
Li2020$year <- 2020

Li2021 <- Li2021 %>%
  rename(ntl = value)
Li2021$year <- 2021

Li2022 <- Li2022 %>%
  rename(ntl = value)
Li2022$year <- 2022
```

##### k = 1
```{r}
buffer_dist <- 1000
Li2013_k1 <- st_buffer(Li2013, dist = buffer_dist)
Li2013_k1$buffer_id <- 1:nrow(Li2013_k1)
buffer_cainiao <- st_intersects(Li2013_k1, poi2013) %>%lengths()
Li2013_k1$parcel_station_count <- buffer_cainiao

Li2014_k1 <- st_buffer(Li2014, dist = buffer_dist)
Li2014_k1$buffer_id <- 1:nrow(Li2014_k1)
buffer_cainiao <- st_intersects(Li2014_k1, poi2014) %>% lengths()
Li2014_k1$parcel_station_count <- buffer_cainiao

Li2015_k1 <- st_buffer(Li2015, dist = buffer_dist)
Li2015_k1$buffer_id <- 1:nrow(Li2015_k1)
buffer_cainiao <- st_intersects(Li2015_k1, poi2015) %>%lengths()
Li2015_k1$parcel_station_count <- buffer_cainiao

Li2016_k1 <- st_buffer(Li2016, dist = buffer_dist)
Li2016_k1$buffer_id <- 1:nrow(Li2016_k1)
buffer_cainiao <- st_intersects(Li2016_k1, poi2016) %>%lengths()
Li2016_k1$parcel_station_count <- buffer_cainiao

Li2017_k1 <- st_buffer(Li2017, dist = buffer_dist)
Li2017_k1$buffer_id <- 1:nrow(Li2017_k1)
buffer_cainiao <- st_intersects(Li2017_k1, poi2017) %>%lengths()
Li2017_k1$parcel_station_count <- buffer_cainiao

Li2018_k1 <- st_buffer(Li2018, dist = buffer_dist)
Li2018_k1$buffer_id <- 1:nrow(Li2018_k1)
buffer_cainiao <- st_intersects(Li2018_k1, poi2018) %>%lengths()
Li2018_k1$parcel_station_count <- buffer_cainiao

Li2019_k1 <- st_buffer(Li2019, dist = buffer_dist)
Li2019_k1$buffer_id <- 1:nrow(Li2019_k1)
buffer_cainiao <- st_intersects(Li2019_k1, poi2019) %>%lengths()
Li2019_k1$parcel_station_count <- buffer_cainiao

Li2020_k1 <- st_buffer(Li2020, dist = buffer_dist)
Li2020_k1$buffer_id <- 1:nrow(Li2020_k1)
buffer_cainiao <- st_intersects(Li2020_k1, poi2020) %>%lengths()
Li2020_k1$parcel_station_count <- buffer_cainiao

Li2021_k1 <- st_buffer(Li2021, dist = buffer_dist)
Li2021_k1$buffer_id <- 1:nrow(Li2021_k1)
buffer_cainiao <- st_intersects(Li2021_k1, poi2021) %>%lengths()
Li2021_k1$parcel_station_count <- buffer_cainiao

Li2022_k1 <- st_buffer(Li2022, dist = buffer_dist)
Li2022_k1$buffer_id <- 1:nrow(Li2022_k1)
buffer_cainiao <- st_intersects(Li2022_k1, poi2022) %>%lengths()
Li2022_k1$parcel_station_count <- buffer_cainiao
```
##### k = 3
```{r}
buffer_dist <- 3000
Li2013_k3 <- st_buffer(Li2013, dist = buffer_dist)
Li2013_k3$buffer_id <- 1:nrow(Li2013_k3)
buffer_cainiao <- st_intersects(Li2013_k3, poi2013) %>%lengths()
Li2013_k3$parcel_station_count <- buffer_cainiao

Li2014_k3 <- st_buffer(Li2014, dist = buffer_dist)
Li2014_k3$buffer_id <- 1:nrow(Li2014_k3)
buffer_cainiao <- st_intersects(Li2014_k3, poi2014) %>%lengths()
Li2014_k3$parcel_station_count <- buffer_cainiao

Li2015_k3 <- st_buffer(Li2015, dist = buffer_dist)
Li2015_k3$buffer_id <- 1:nrow(Li2015_k3)
buffer_cainiao <- st_intersects(Li2015_k3, poi2015) %>%lengths()
Li2015_k3$parcel_station_count <- buffer_cainiao

Li2016_k3 <- st_buffer(Li2016, dist = buffer_dist)
Li2016_k3$buffer_id <- 1:nrow(Li2016_k3)
buffer_cainiao <- st_intersects(Li2016_k3, poi2016) %>%lengths()
Li2016_k3$parcel_station_count <- buffer_cainiao

Li2017_k3 <- st_buffer(Li2017, dist = buffer_dist)
Li2017_k3$buffer_id <- 1:nrow(Li2017_k3)
buffer_cainiao <- st_intersects(Li2017_k3, poi2017) %>%lengths()
Li2017_k3$parcel_station_count <- buffer_cainiao

Li2018_k3 <- st_buffer(Li2018, dist = buffer_dist)
Li2018_k3$buffer_id <- 1:nrow(Li2018_k3)
buffer_cainiao <- st_intersects(Li2018_k3, poi2018) %>%lengths()
Li2018_k3$parcel_station_count <- buffer_cainiao

Li2019_k3 <- st_buffer(Li2019, dist = buffer_dist)
Li2019_k3$buffer_id <- 1:nrow(Li2019_k3)
buffer_cainiao <- st_intersects(Li2019_k3, poi2019) %>%lengths()
Li2019_k3$parcel_station_count <- buffer_cainiao

Li2020_k3 <- st_buffer(Li2020, dist = buffer_dist)
Li2020_k3$buffer_id <- 1:nrow(Li2020_k3)
buffer_cainiao <- st_intersects(Li2020_k3, poi2020) %>%lengths()
Li2020_k3$parcel_station_count <- buffer_cainiao

Li2021_k3 <- st_buffer(Li2021, dist = buffer_dist)
Li2021_k3$buffer_id <- 1:nrow(Li2021_k3)
buffer_cainiao <- st_intersects(Li2021_k3, poi2021) %>%lengths()
Li2021_k3$parcel_station_count <- buffer_cainiao

Li2022_k3 <- st_buffer(Li2022, dist = buffer_dist)
Li2022_k3$buffer_id <- 1:nrow(Li2022_k3)
buffer_cainiao <- st_intersects(Li2022_k3, poi2022) %>%lengths()
Li2022_k3$parcel_station_count <- buffer_cainiao
```

##### k = 5
```{r}
buffer_dist <- 5000
Li2013_k5 <- st_buffer(Li2013, dist = buffer_dist)
Li2013_k5$buffer_id <- 1:nrow(Li2013_k5)
buffer_cainiao <- st_intersects(Li2013_k5, poi2013) %>%lengths()
Li2013_k5$parcel_station_count <- buffer_cainiao

Li2014_k5 <- st_buffer(Li2014, dist = buffer_dist)
Li2014_k5$buffer_id <- 1:nrow(Li2014_k5)
buffer_cainiao <- st_intersects(Li2014_k5, poi2014) %>%lengths()
Li2014_k5$parcel_station_count <- buffer_cainiao

Li2015_k5 <- st_buffer(Li2015, dist = buffer_dist)
Li2015_k5$buffer_id <- 1:nrow(Li2015_k5)
buffer_cainiao <- st_intersects(Li2015_k5, poi2015) %>%lengths()
Li2015_k5$parcel_station_count <- buffer_cainiao

Li2016_k5 <- st_buffer(Li2016, dist = buffer_dist)
Li2016_k5$buffer_id <- 1:nrow(Li2016_k5)
buffer_cainiao <- st_intersects(Li2016_k5, poi2016) %>%lengths()
Li2016_k5$parcel_station_count <- buffer_cainiao

Li2017_k5 <- st_buffer(Li2017, dist = buffer_dist)
Li2017_k5$buffer_id <- 1:nrow(Li2017_k5)
buffer_cainiao <- st_intersects(Li2017_k5, poi2017) %>%lengths()
Li2017_k5$parcel_station_count <- buffer_cainiao

Li2018_k5 <- st_buffer(Li2018, dist = buffer_dist)
Li2018_k5$buffer_id <- 1:nrow(Li2018_k5)
buffer_cainiao <- st_intersects(Li2018_k5, poi2018) %>%lengths()
Li2018_k5$parcel_station_count <- buffer_cainiao

Li2019_k5 <- st_buffer(Li2019, dist = buffer_dist)
Li2019_k5$buffer_id <- 1:nrow(Li2019_k5)
buffer_cainiao <- st_intersects(Li2019_k5, poi2019) %>%lengths()
Li2019_k5$parcel_station_count <- buffer_cainiao

Li2020_k5 <- st_buffer(Li2020, dist = buffer_dist)
Li2020_k5$buffer_id <- 1:nrow(Li2020_k5)
buffer_cainiao <- st_intersects(Li2020_k5, poi2020) %>%lengths()
Li2020_k5$parcel_station_count <- buffer_cainiao

Li2021_k5 <- st_buffer(Li2021, dist = buffer_dist)
Li2021_k5$buffer_id <- 1:nrow(Li2021_k5)
buffer_cainiao <- st_intersects(Li2021_k5, poi2021) %>%lengths()
Li2021_k5$parcel_station_count <- buffer_cainiao

Li2022_k5 <- st_buffer(Li2022, dist = buffer_dist)
Li2022_k5$buffer_id <- 1:nrow(Li2022_k5)
buffer_cainiao <- st_intersects(Li2022_k5, poi2022) %>%lengths()
Li2022_k5$parcel_station_count <- buffer_cainiao
```

##### combine dataset
```{r}
buffer_k1 <- bind_rows(Li2013_k1, Li2014_k1, Li2015_k1, Li2016_k1, Li2017_k1, Li2018_k1, Li2019_k1, Li2020_k1, Li2021_k1, Li2022_k1)
buffer_k1$nearest_station_distance <- nearest_dis$nearest_station_distance

buffer_k3 <- bind_rows(Li2013_k3, Li2014_k3, Li2015_k3, Li2016_k3, Li2017_k3, Li2018_k3, Li2019_k3, Li2020_k3, Li2021_k3, Li2022_k3)

buffer_k5 <- bind_rows(Li2013_k5, Li2014_k5, Li2015_k5, Li2016_k5, Li2017_k5, Li2018_k5, Li2019_k5, Li2020_k5, Li2021_k5, Li2022_k5)
```

# OLS
```{r}
OLS_k1 <- lm(ntl ~ parcel_station_count, data = buffer_k1)
OLS_k3 <- lm(ntl ~ parcel_station_count, data = buffer_k3)
OLS_k5 <- lm(ntl ~ parcel_station_count, data = buffer_k5)

OLS_nearest <- lm(ntl ~ nearest_station_distance, data = nearest_dis)

summary(OLS_nearest)
summary(OLS_k1)
summary(OLS_k3)
summary(OLS_k5)
```

# panel data
```{r}
panel_data_k1 <- pdata.frame(buffer_k1, index = c("buffer_id", "year"))
panel_data_k3 <- pdata.frame(buffer_k3, index = c("buffer_id", "year"))
panel_data_k5 <- pdata.frame(buffer_k5, index = c("buffer_id", "year"))
```

## fixed effects
panel_k1 <- plm(ntl ~ parcel_station_count + factor(year), data = panel_data_k1, model = "within")
panel_k3 <- plm(ntl ~ parcel_station_count + factor(year), data = panel_data_k3, model = "within")
panel_k5 <- plm(ntl ~ parcel_station_count + factor(year), data = panel_data_k5, model = "within")

panel_nearest <- plm(ntl ~ nearest_station_distance + factor(year), data = panel_data_k1, model = "within")

summary(panel_k1)
summary(panel_k3)
summary(panel_k5)
summary(panel_nearest)

limitation: parcel station count is too small for the panel data analysis. Not suitable in this model. 
```{r}
panel_nearest <- plm(ntl ~ nearest_station_distance + factor(year), data = panel_data_k1, model = "within")
summary(panel_nearest)
```

## count data
Negative Binomial Regression
```{r}
mean_value <- mean(panel_data_k1$parcel_station_count, na.rm = TRUE)
variance_value <- var(panel_data_k1$parcel_station_count, na.rm = TRUE)

mean_value
variance_value
summary(panel_data_k1$parcel_station_count)
```


```{r}
# Negative Binomial Regression
negbin_k1 <- fenegbin(ntl ~ parcel_station_count | year, data = panel_data_k1)
negbin_k3 <- fenegbin(ntl ~ parcel_station_count | year, data = panel_data_k3)
negbin_k5 <- fenegbin(ntl ~ parcel_station_count | year, data = panel_data_k5)

summary(negbin_k1)
summary(negbin_k3)
summary(negbin_k5)
```

# pooled OLS
```{r}
buffer_k1$buffer_id <- as.factor(buffer_k1$buffer_id)
buffer_k1$year <- as.factor(buffer_k1$year)

buffer_k3$buffer_id <- as.factor(buffer_k3$buffer_id)
buffer_k3$year <- as.factor(buffer_k3$year)

buffer_k5$buffer_id <- as.factor(buffer_k5$buffer_id)
buffer_k5$year <- as.factor(buffer_k5$year)

# Pooled OLS
pooled_ols_lm_nearest <- lm(ntl ~ nearest_station_distance, data = buffer_k1)
pooled_ols_lm_k1 <- lm(ntl ~ parcel_station_count, data = buffer_k1)
pooled_ols_lm_k3 <- lm(ntl ~ parcel_station_count, data = buffer_k3)
pooled_ols_lm_k5 <- lm(ntl ~ parcel_station_count, data = buffer_k5)

pooled_ols_plm_k1 <- plm(ntl ~ parcel_station_count, data = panel_data_k1, model = "pooling")
pooled_ols_plm_k3 <- plm(ntl ~ parcel_station_count, data = panel_data_k3, model = "pooling")
pooled_ols_plm_k5 <- plm(ntl ~ parcel_station_count, data = panel_data_k5, model = "pooling")

summary(pooled_ols_lm_nearest)
summary(pooled_ols_lm_k1)
summary(pooled_ols_plm_k1)
summary(pooled_ols_plm_k3)
summary(pooled_ols_plm_k5)
```

# Lag effects
```{r}
panel_lag_data_k1 <- as.data.table(panel_data_k1)
panel_lag_data_k3 <- as.data.table(panel_data_k3)
panel_lag_data_k5 <- as.data.table(panel_data_k5)

panel_lag_data_nearest <- panel_lag_data_k1[order(buffer_id, year)]
panel_lag_data_nearest[, nearest_lag1 := shift(nearest_station_distance, 1, type = "lag"), by = buffer_id]
panel_lag_data_nearest[, nearest_lag2 := shift(nearest_station_distance, 2, type = "lag"), by = buffer_id]
panel_lag_data_nearest[, nearest_lag3 := shift(nearest_station_distance, 3, type = "lag"), by = buffer_id]

panel_lag_data_k1 <- panel_lag_data_k1[order(buffer_id, year)]
panel_lag_data_k1[, Station_lag1 := shift(parcel_station_count, 1, type = "lag"), by = buffer_id]
panel_lag_data_k1[, Station_lag2 := shift(parcel_station_count, 2, type = "lag"), by = buffer_id]
panel_lag_data_k1[, Station_lag3 := shift(parcel_station_count, 3, type = "lag"), by = buffer_id]

panel_lag_data_k3 <- panel_lag_data_k3[order(buffer_id, year)]
panel_lag_data_k3[, Station_lag1 := shift(parcel_station_count, 1, type = "lag"), by = buffer_id]
panel_lag_data_k3[, Station_lag2 := shift(parcel_station_count, 2, type = "lag"), by = buffer_id]
panel_lag_data_k3[, Station_lag3 := shift(parcel_station_count, 3, type = "lag"), by = buffer_id]

panel_lag_data_k5 <- panel_lag_data_k5[order(buffer_id, year)]
panel_lag_data_k5[, Station_lag1 := shift(parcel_station_count, 1, type = "lag"), by = buffer_id]
panel_lag_data_k5[, Station_lag2 := shift(parcel_station_count, 2, type = "lag"), by = buffer_id]
panel_lag_data_k5[, Station_lag3 := shift(parcel_station_count, 3, type = "lag"), by = buffer_id]
```

```{r}
# remove geometry
panel_lag_data_nearest <- panel_lag_data_nearest %>%
  dplyr::select(-geometry)
panel_lag_data_k1 <- panel_lag_data_k1 %>%
  dplyr::select(-geometry)
panel_lag_data_k3 <- panel_lag_data_k3 %>%
  dplyr::select(-geometry)
panel_lag_data_k5 <- panel_lag_data_k5 %>%
  dplyr::select(-geometry)

# pdata.frame
panel_lag_data_nearest <- pdata.frame(panel_lag_data_nearest, index = c("buffer_id", "year"))
panel_lag_data_k1 <- pdata.frame(panel_lag_data_k1, index = c("buffer_id", "year"))
panel_lag_data_k3 <- pdata.frame(panel_lag_data_k3, index = c("buffer_id", "year"))
panel_lag_data_k5 <- pdata.frame(panel_lag_data_k5, index = c("buffer_id", "year"))
```

```{r}
# negative binomial with fixed effects
lag_nearest <- plm(ntl ~ nearest_station_distance + nearest_lag1 + nearest_lag2 + nearest_lag3 + factor(year), data = panel_lag_data_nearest)

lag_k1 <- fenegbin(ntl ~ parcel_station_count + Station_lag1 +Station_lag2 + Station_lag3 | year, data = panel_lag_data_k1)
lag_k3 <- fenegbin(ntl ~ parcel_station_count + Station_lag1 +Station_lag2 + Station_lag3 | year, data = panel_lag_data_k3)
lag_k5 <- fenegbin(ntl ~ parcel_station_count + Station_lag1 +Station_lag2 + Station_lag3 | year, data = panel_lag_data_k5)

summary(lag_nearest)
summary(lag_k1)
summary(lag_k3)
summary(lag_k5)
```
